The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

The key explanatory variable will be the degree of self confidence. We will compute an index from both OECD PISA, World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).

>>>>

The key explanatory variable will be the degree of self confidence. As we did not find so far any satisfactory proxy for self-confidence in the way we intend to define it, we will need to compute an index. In order to do so, we will rely on both OECD PISA, World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).

V86   How important are adventure and taking risks to the person surveyed?
V119 How good is competition?

Please note that data was collected at different dates in Britain (2005) and in France (2006), but in both cases before the economic crisis, which may have affected people’s prospects and values.

As we mentioned that self-confidence also depends on the integration in social networks, we will rely on the sense of belonging as defined by OECD PISA study. Again we will need to compute an index. In order to do so, we will also rely on the following items from the World Value Survey 2005-2009 wave about “sense of belonging to a group“ and “sense of individuality” and “degree of self confidence”.

V65   I seek to be myself rather than to follow others
V66   I live up to what my friends expect
V67   I decide my goals in life by myself
V78   How good / bad is greater respect for authority to the person surveyed?
V186 How often do you attend religious services?
V198 How justifiable can claiming government benefits be?
V199 How justifiable can avoiding a fare on public transport be?
V200 How justifiable can cheating on taxes be?
